\documentclass[11pt]{article}


\usepackage{amsfonts}
\usepackage{url}


\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\headsep}{0.5in}
\setlength{\textheight}{8.5in}
\setcounter{page}{1}
%\pagestyle{empty}
%\hbadness=10000


\begin{document}
\huge
\noindent
{Discrete Optimization Assignment:}
\vspace{0.25cm}

\noindent
{\bf Screen Name}
\normalsize


\section{Problem Statement}
This assignment is designed to familiarize you with the programming assignment infrastructure.  All of the assignments in this class involve writing an optimization algorithm (i.e. a program) and submitting your results with the provided submission script.  In this assignment, you will write a very simple program to submit a {\em screen name} of your choice to the course.  In future assignments, your screen name will be used when presenting your results on a leader board.

\section{Assignment}

Write an algorithm to submit your screen name to the course.  The screen names are {\it not} required to be unique.  If you have difficulty finding your results in the leader board, resubmit this assignment to change your name to something more unique.

\section{Data Format Specification}

The output is one line containing your screen name, $s$.
%
\begin{verbatim}[Output Format]
s
\end{verbatim}
%
The screen name can only contain letters, numbers, spaces, dashes, and underscores (i.e.\texttt{\_}).  It should also be no more than 40 characters long (including spaces).

\paragraph{Examples}

\begin{verbatim}[Output Example]
C4rl3t0n
\end{verbatim}

\begin{verbatim}[Output Example]
The Optimizer
\end{verbatim}

\begin{verbatim}[Output Example]
734562234
\end{verbatim}

\section{Instructions}

Edit \texttt{solver.py} and modify the \texttt{solve\_it()} function to return your screen name.  Your \texttt{solve\_it} implementation can be tested with the command \texttt{python ./solver.py}

\paragraph{Handin}
Run \texttt{submit.py} with the command,
\texttt{python ./submit.py}\\
Follow the instructions to submit your screen name.  You can submit multiple times.  However, it may take several minutes before your screen name is updated.

%\paragraph{Questions} Please contact the class GTA Carleton (cjc@cs.brown.edu).

%\paragraph{Warning} This is a first time assignment, be prepared for clarifications and bug-fixes.

\input{techReqs.tex}

\end{document}




