\documentclass[11pt]{article}


\usepackage{amsfonts}
\usepackage{fancyvrb}
\usepackage{url}

\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\headsep}{0.5in}
\setlength{\textheight}{8.5in}
\setcounter{page}{1}
%\pagestyle{empty}
%\hbadness=10000

\begin{document}
\huge
\noindent
{Discrete Optimization Assignment:}
\vspace{0.25cm}

\noindent
{\bf Knapsack}
\normalsize


\section{Problem Statement}

In this assignment you will design an algorithm to solve the infamous {\em Knapsack Problem}, which plagues Indiana Jones.  You are provided with a knapsack with limited space and a collection of items with different values and weights.  Your task is to maximize the value of items packed into your knapsack without exceeding its total capacity.

\section{Assignment}

Write an algorithm to solve the knapsack problem.  The problem is mathematically formulated in the following way.  Given $n$ items to choose from, each item $i \in 0 \ldots n-1$ has a value $v_i$ and a weight $w_i$.  The knapsack has a limited capacity $K$.  Let $x_i$ be a variable that is $1$ if you choose to take item $i$ and $0$ if you leave item $i$ behind. Then the knapsack problem is formalized as the following optimization problem,
$$
\begin{array}{ll}
\mbox{maximize:} & \displaystyle \sum_{i \in 0 \ldots n-1} v_i x_i \\
\mbox{subject to:} & \\
     & \displaystyle \sum_{i \in 0 \ldots n-1} w_i x_i \leq K \\
     & x_i \in \{0,1\} \;\;\; (i \in 0 \ldots n-1)
\end{array}
$$

\section{Data Format Specification}

A knapsack input contains $n+1$ lines.  The first line contains two integers, the first is the number of items in the problem, $n$.  The second number is the capacity of the knapsack, $K$.  The remaining lines present the data for each of the items.  Each line, $i \in 0 \ldots n-1$ contains two integers, the item's value $v_i$ followed by its weight $w_i$.

\vspace{0.2cm}
\noindent
Input Format
\vspace{-0.2cm}
\begin{Verbatim}[frame=single]
n K
v_0 w_0
v_1 w_1
...
v_n-1 w_n-1
\end{Verbatim}
%
The output contains a knapsack solution and is made of two lines.  The first line contains two values $obj$ and $opt$.  $obj$ is the total value of the items selected to go into the knapsack (i.e. the objective value).  $opt$ should be $1$ if your algorithm proved optimality and $0$ otherwise.  The next line is a list of $n$ $0/1$-values, one for each of the $x_i$ variables.  This line encodes the solution.
\clearpage
%
\vspace{0.2cm}
\noindent
Output Format
\vspace{-0.2cm}
\begin{Verbatim}[frame=single]
obj opt
x_0 x_1 x_2 ... x_n-1
\end{Verbatim}
%
It is essential that the value order in the solution output matches the value order of the input.  Otherwise the grader will misinterpret the output.

\paragraph{Examples} \mbox{}
%\vspace{0.1cm}

\vspace{0.2cm}
\noindent
Input Example
\vspace{-0.2cm}
\begin{Verbatim}[frame=single]
4 11
8 4
10 5
15 8
4 3
\end{Verbatim}

\vspace{0.2cm}
\noindent
Output Example
\vspace{-0.2cm}
\begin{Verbatim}[frame=single]
19 0
0 0 1 1
\end{Verbatim}

\section{Instructions}

%Edit \texttt{solver.py} and modify the \texttt{solveIt(inputData)} function to solve the knapsack problem.  The function argument, \texttt{inputData}, contains a knapsack problem in the format described above.  The return value of \texttt{solveIt} is a solution to the problem in the output format described above.  Your \texttt{solveIt} implementation can be tested with the command, 
%\[ 
%\texttt{python ./solver.py ./data/<inputFileName>} 
%\] 
%You should limit the \texttt{solveIt} method to terminate within 5 hours, otherwise the submission will not be eligible for full credit.  You may choose to implement your solver directly in python or modify the \texttt{solveIt()} function to call an external application.

\input{instructions.tex}

\paragraph{Resources}
You will find several knapsack instances in the \texttt{data} directory provided with the handout.  \texttt{Solver.java} and \texttt{solverJava.py} are included in this assignment to demonstrate how to implement your assignment in another language.  If you wish to use the Java solver, you will need to rename \texttt{solverJava.py} to \texttt{solver.py}.
%An example output file, \texttt{blabla.out}, is also provided.

%\section{Remarks}

\input{handin.tex}

\input{grading.tex}

\input{collaboration.tex}

%\paragraph{Questions} Please contact the class GTA Carleton (cjc@cs.brown.edu).

\input{warnings.tex}

%\paragraph{Warnings} 
%
%\begin{enumerate}
%\item It is recommended you do not modify the \texttt{data} directory.  Modifying the files in the data directory risks
%making your assignment submissions incorrect.
%\item You cannot rename the \texttt{solver.py} file.
%\item \texttt{solver.py} must remain in the same directory as  \texttt{submit.pyc}.
%\end{enumerate}

\input{techReqs.tex}

\end{document}




